Second-Generation Web Interface to Correcting ASR output

### 2018-03-31 2018-ftc-vancouver/webapp.tex
stop pretending we aren't we

Kr\r{u}za 2012\cite{kruuza2012making} presented a setting where a community of
users contributed corrections to automatically transcribed talks of a single
speaker. Now that the browser technologies evolved drastically and we could
observe the usage patterns and discover shortcomings of the solution at hand, we
have created a next generation of the programme. We shall describe the steps
taken and discuss their motivation and impact.

@@

Kr\r{u}za 2012~\cite{kruuza2012making} solve this by sacrificing point~5:
only 3 lines of text are shown with the current word kept on the middle line as
shown on Figure~\ref{fig:makonfm}.\footnote{The current word is on the top line
on the screenshot because it is at the beginning of the recording.} Thanks to
the development in the web standards and their support from popular browsers, a
solution is possible.

>>>>

In 2012\cite{kruuza2012making}, we have presented a setting where a community of
users contributed corrections to automatically transcribed talks of a single
speaker. Now that the browser technologies evolved drastically and we could
observe the usage patterns and discover shortcomings of the solution at hand, we
have created a next generation of the programme. We shall describe the steps
taken and discuss their motivation and impact.

@@

In the original version, we solved this by sacrificing point~5:
only 3 lines of text are shown with the current word kept on the middle line as
shown on Figure~\ref{fig:makonfm}.\footnote{The current word is on the top line
on the screenshot because it is at the beginning of the recording.} Thanks to
the development in the web standards and their support from popular browsers, a
solution is possible.
